---
title: "Pedagogy_Final_RCode"
author: "Joshua Cabrera"
date: "2024-02-25"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidyverse)
library(caret)
library(GGally) #pairs plot
library(car) #added variable plots
library(MASS) #standardized Residuals
library(lmtest) #bp test
library(multcomp) #generalized linear hypothesis test
library(nlme)
library(tidyverse)
data  <- read_delim('ClassAssessment.txt')
data_copy <- data
data$Semester <- as.factor(data$Semester)
```


# Section 1 
## A
```{r}
pairs(data[,3:6])
pairs(data)



```
```{r}
ggplot(data, aes(x = Semester, y = Final, fill = Semester)) +
  geom_boxplot() +
  labs(x = "Semester", y = "Final", title = "Box Plot Example") +
  theme_minimal()

```
```{r}

data_long <- data_copy %>%
  pivot_longer(
    cols = c(Exam1, Exam2, Exam3,HW,Quiz, Final) )

data_copy$id <- 1:30

data_long$factor_column <- factor(data_long$name)
data_long$factor_column <- factor(data_long$name, levels = c("Exam1", "Exam2", "Exam3", "HW", "Quiz", "Final"))

levels(data_long$factor_column)

# head(data_long)
ggplot(data_long, aes(x = name, y = value, group = id, colour = id))+
  geom_point()+
  geom_line()
```

## B
Discuss any potential issues associated with the data that you should make sure to account for in 
your analysis.

Variance should be divided by NStudents, but I don't quite understand why.

##C
For any issues identified above, discuss the consequences of ignoring these issues in an analysis 
along with any benefits gained by accounting for these issues.

I don't understand why this is an issue.

## D

Variance divided by NStudents? Why?

```{r}
# summary(data)



# Pedagogy_lm <- lm(Final ~ ., data = data)
Pedagogy_lm <- lm(Final ~ ., data = data)
summary(Pedagogy_lm)

#Checking if our model should use NStudents and Semester
Pedagogy_lm_reduced <- lm(Final ~ Exam1+Exam2+Exam3+HW+Quiz, data = data)
summary(Pedagogy_lm_reduced)
anova(Pedagogy_lm_reduced,Pedagogy_lm)

#using reduced model and changing name
Pedagogy_lm <- lm(Final ~ Exam1+Exam2+Exam3+HW+Quiz, data = data)
summary(Pedagogy_lm)


data_copy$fittedVals <- Pedagogy_lm$fitted.values
data_copy$Residuals <- Pedagogy_lm$residuals

# write.csv(data, file = "ClassAssessment_copy.txt", row.names =T)

#none of the semesters performed better than other semesters
anova_result <- aov(lm(Final ~ Semester, data = data))
anova_result
summary(anova_result)
# anova_result <- anova(lm(value ~ group, data = df))

```


